Processing of visual and non-visual naturalistic spatial information in the "parahippocampal place area"

### 2021-02-19 paper/main.tex
More cleanup

\noindent General
\begin{itemize}
    \item van den Hurk (2017): uses sounds (1.8sec); one-back-task; no
        significant results; but ``sensitivity maps'' and cross-modal and
        cross-subject classification; mentions in a half sentence ``the auditory
        trials might activate only a subset of voxels that contain categorical
        information, whereas the visual trials activate the majority of VTC
        voxels''.
\end{itemize}

\noindent Method

\begin{itemize}
    \item Fig regressor correlations: maybe write out in full the name of
        regressors (instead of pointing to the table)
    \item different frame counts of segments AV vs. AD
\end{itemize}

\noindent Results

\begin{itemize}
    \item tables: I (initially) rounded p-values to <.00001
\end{itemize}

\noindent Discussion
\begin{itemize}
    \item "Lokalisation der PPA" vs. "Antwortverhalten einer vorab definierten
        PPA". Machst wohl das erste, beschreibst es aber als das zweite
\end{itemize}

@@

\noindent Data Citations, Code Availability
\begin{itemize}
    \item draft for Data Citation is done
    \item draft for Code and Data Availability is done (other analysis paper do
        it pretty amateurish); will look at the ``how to write an excellent
        data availability statement'' at springernature.com
\end{itemize}

@@

% literature review overview 1: imagination & haptic exploration
Increased hemodynamic activity in the PPA generalizes to mental imagination of
landscapes \citep{ocraven2000mental}, haptic exploration of scenes
constructed from LEGO blocks \citep{wolbers2011modality} and scene-related
sounds \citep{van2017development}.\todo{reading the paper: activation is
non-significant, lol}
% van der Hurk: 64 sounds x 1.8 seconds; 20 sighted, 14 congenitally blind
\todo{cite Lescroart (2019). semi-naturalistic, but task, 800+ stimulus, N=6}
% O'Craven: watching pictures
In a study conducted by \cite{ocraven2000mental} participants viewed alternating
blocks of pictures showing familiar places and famous faces during an initial
experimental paradigm.
% O'Craven: mental imagery
In a subsequent paradigm, participants were instructed to ``form a vivid mental
image'' of the previously viewed pictures.
% O'Craven results
The PPA showed increased activation during imagination of places compared to
faces but the imagination tasks showed a smaller activation level compared to
the perceptual task.
% Wolbers: haptic exploration
In a block design study conducted by \cite{wolbers2011modality} the PPA of
sighted as well as blind participants showed increased activation during a
delayed match-to-sample task of haptically explored scenes constructed from LEGO
bricks compared to abstract geometric objects.
% Wolbers: connectivity analysis

>>>>

@@

\noindent Data Citations, Code Availability
\begin{itemize}
    \item draft for Code and Data Availability is done (other analysis paper do
        it pretty amateurish); will look at the ``how to write an excellent
        data availability statement'' at springernature.com
\end{itemize}

@@

% literature review overview 1: imagination & haptic exploration
Increased hemodynamic activity in the PPA generalizes to mental imagination of
landscapes \citep{ocraven2000mental}, haptic exploration of scenes
constructed from LEGO blocks \citep{wolbers2011modality} and scene-related
sounds \citep{van2017development}.
% van der Hurk: 64 sounds x 1.8 seconds; 20 sighted, 14 congenitally blind
\todo{cite Lescroart (2019). semi-naturalistic, but task, 800+ stimulus, N=6}
% O'Craven: watching pictures
In a study conducted by \cite{ocraven2000mental} participants viewed alternating
blocks of pictures showing familiar places and famous faces during an initial
experimental paradigm.
% O'Craven: mental imagery
In a subsequent paradigm, participants were instructed to ``form a vivid mental
image'' of the previously viewed pictures.
% O'Craven results
The PPA showed increased activation during imagination of places compared to
faces but the imagination tasks showed a smaller activation level compared to
the perceptual task.
% Wolbers: haptic exploration
In a block design study conducted by \cite{wolbers2011modality} the PPA of
sighted as well as blind participants showed increased activation during a
delayed match-to-sample task of haptically explored scenes constructed from LEGO
bricks compared to abstract geometric objects.
% Wolbers: connectivity analysis
